Membrane-localized Keratin-14 Promotes Invasion\thanks{Supported by organization x.}

### 2018-12-06 docs/01_paper/paper.tex
Added a way to generate figures and added figure 1
Updates from ShareLaTeX
Added Joel's recommended template

Alternative title: Morphological features of organoid invasion are correlated to membrane-localized Keratin-14 expression

@@

@@

\textcolor{blue}{
\begin{itemize}
    \item Experimental protocol. Ask Veena to write this part.\\ 
        100-300 organoids from 4 mice.
    \item Image acquisition and organoid periphery. Veena.\\
        Use ImageJ to mark the periphery of the organoids from DCI microscop images.
    \item Image segmentation. Andrei to write about convolution kernel.
    \item Spectral score. Reference Joel's paper. Disclose scripts?
\end{itemize}
}

\subsection{Database}

@@

\subsection{Spectral Analysis}

\subsubsection{}

@@

@@

\section{Discussion}

Future directions: Test our method on Patient derived organoids, PDOs.\\
Does organoid invasion score correlate with patient outcome?

>>>>

Alternative title: Morphological features of organoid invasion are correlated with membrane-localized Keratin-14 expression

@@

Previous observation from Ewald group about K14 expression.

@@

\textcolor{blue}{
\begin{itemize}
    \item Experimental protocol. Ask Veena to write this part.\\ 
        100-300 organoids from 4 mice.
    \item Image acquisition and organoid periphery. Veena.\\
        Use ImageJ to mark the periphery of the organoids from DIC microscope images.
    \item Image segmentation. Andrei to write about convolution kernel.
    \item Spectral score. Reference Joel's paper. Disclose scripts?
\end{itemize}
}

\subsection{Data acquisition}

@@

\subsection{Spectral Analysis}
A method described in REF.\\
Able to distinguish quantitative phenotypes.

\subsection{Convolution kernel}
ANDREI

\subsection{Correlation Analysis}

\begin{figure}
\includegraphics[width=\textwidth]{Image1.pdf}
\caption{Displays the K14 Image, DIC image, Bounday and spectral power analysis plots for three different organoids. \textcolor{red}{Axis font needs to be bigger. Y-axis in spectral score should all be the same and we can probably skip column 2.}} \label{fig1}
\end{figure}

@@

\begin{table}
\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (PyMMT mice) & 	1 & 2 & 3 & 4 \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.39} & \textbf{0.43} & \textbf{0.29} & \textbf{0.123} \\
			 \hline
			 Centeral sum K14 & 0.21 & 0.19 & 0.11 & 0.010 \\
			 \hline
			 Entire sum K14 & 0.22 & 0.22 & 0.12 & 0.013 \\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 \\ [1ex]
%			 \hline
			Organoid size & 0.27 & 0.33 & 0.27 & 0.076 \\
			 \hline
		\end{tabular}
		}
\end{table}

\begin{table}
\caption{Peripheral K14 explains correlates with invasive potential the best.}\label{tab1}
		\centering
		\resizebox{0.8\textwidth}{!}{
		 \begin{tabular}{||l c c c c||}
			\hline
			 & \multicolumn{4}{|c|}{$r^2$ by mouse} \\
			 \hline
			 Organoids (C3(1)tag mice) & 1 & 2 & 3 & 4  \\ [0.5ex]
			 \hline\hline
			  \textbf{Peripheral sum K14} & \textbf{0.11} & \textbf{0.25} & 0.06 & 0.03 \\
			 \hline
			 Centeral sum K14 & 0.01 & 0.03 & 0.06 & 0.00\\
			 \hline
			 Entire sum K14 & 0.01 & 0.00 & 0.01 & 0.00\\
			 \hline
%			 K14 Mean & 0.02 & 0.04 & 0.03 & xx\\ [1ex]
%			 \hline
			Organoid size & 0.07 & 0.01 & \textbf{0.07} &  \textbf{0.06} \\
			 \hline
		\end{tabular}
		}
\end{table}

@@

\section{Discussion}
We implemented a method to quanitfy the invasive phenotypes organoids derived from two distinct mouse models, namely PyMT and C3(1)tag.\\
Out of the features we tested, we found that peripheral K14 expression correlated with the invasive phenotype.\\
Why is this important and/or interesting?\\
Future directions: Test our method on Patient derived organoids, PDOs.\\
Does organoid invasion score correlate with patient outcome?
